### 2020-03-04 README.Rmd
tidy up readme, `retrieve` -> `resolve`

---
output: github_document
---

@@

The `retrieve()` verb (subject to change), provides a wrapper around `query` that always returns exactly one local path to requested content.  It will check for a stored copy of the content first, and download (and verify) remote content otherwise:

```{r}
path <- retrieve("hash://sha256/9412325831dab22aeebdd674b6eb53ba6b7bdd04bb99a4dbb21ddff646287e37")
```

@@

```{r}
readLines(path, n = 10)
## we could manually verify identity, though retrieve has already done this:

content_uri(path)
```

>>>>

---
output: 
  github_document:
    df_print: tibble
---

@@

The `resolve()` verb (subject to change), provides a wrapper around `query` that 'resolves' the content identifier to the content.  It will check for a locally stored copy of the content first, and download (and verify) remote content otherwise:

```{r}
path <- resolve("hash://sha256/9412325831dab22aeebdd674b6eb53ba6b7bdd04bb99a4dbb21ddff646287e37")
```

@@

```{r}
readLines(path, n = 10)
```
